---
title: "Quiz 3"
author: "Aaron Brown"
date: "May 2, 2016"
output: pdf_document
---

# Question 1  
```{r}
#load the cell segmentation data
library(AppliedPredictiveModeling)
data(segmentationOriginal)
library(caret)
require(rattle)
# require(rpart.plot)

set.seed(125)

split <- segmentationOriginal$Case == 'Train'

training = segmentationOriginal[split,]
testing = segmentationOriginal[!split,]

modelFit = train(Class ~ ., method = "rpart", data = training, control = rpart.control(maxdepth = 4L))
fancyRpartPlot(modelFit$finalModel)
```

Answer:  
  A. PS  
  B. WS  
  C. PS  
  D. Not possible to predict  
    
# Question 2  
Answer:  (See Slide 8/8 on cross-validation in Week 1)  The bias is larger and the variance is smaller. Under leave one out cross validation K is equal to the sample size. 

# Question 3  
```{r}
library(caret)
library(pgmm)
data(olive)
olive = olive[,-1]

newdata = as.data.frame(t(colMeans(olive)))

modelFit = train(Area ~ ., method = 'rpart', data = olive)
a3 <- predict(modelFit, newdata)
```

Answer: `r a3'

# Question 4  
```{r}
library(ElemStatLearn)
data(SAheart)
set.seed(8484)
train = sample(1:dim(SAheart)[1],size=dim(SAheart)[1]/2,replace=F)
trainSA = SAheart[train,]
testSA = SAheart[-train,]

set.seed(13234)

modelFit = train(chd ~ age + alcohol + obesity + tobacco + typea + ldl, method = 'glm', 
                 family = 'binomial', data = trainSA)

train.pred = predict(modelFit, trainSA)
test.pred  = predict(modelFit, testSA)

missClass = function(values,prediction){
    sum(((prediction > 0.5)*1) != values)/length(values)}

missClass(testSA$chd,  test.pred)
missClass(trainSA$chd, train.pred)
```

Answer: 

# Question 5  
```{r}
library(ElemStatLearn)
library(caret)
data(vowel.train)
data(vowel.test)

set.seed(33833)

vowel.train$y = as.factor(vowel.train$y)
vowel.test$y = as.factor(vowel.test$y)

modelFit = train(y ~ ., method = 'rf', data = vowel.train)

varImp(modelFit$finalModel)

```

Answer:  According to the quiz, the correct answer of the order begins x.2, x.1,...

My answer begins with x.1, x.2,...  and ends the same.  I'm not sure why...